

\documentclass{acm_proc_article-sp}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}

\renewcommand{\algorithmicrequire}{\textbf{input: }}
\renewcommand{\algorithmicensure}{\textbf{output: }}
\newcommand{\mr}[1]{{\it MR: {\small #1}}}
\newcommand{\eat}[1]{}

\begin{document}

\title{How stories evolve: News graphs as a way to represent context and evolution of news stories}

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
%
% 1st. author
%\alignauthor 
%Rahul Goyal, Ravee Malla, Amitabha Bagchi, Sameep Mehta, Maya Ramanath\\
%  \affaddr{Indian Institute of Technology}\\
%  \affaddr{New Delhi, India}\\
%  \email{\{rahulgoyal34, ravmalla\}@gmail.com, \{bagchi, ramanath\}@cse.iitd.ernet.in}
% 2nd author
%\alignauthor 
%Author 2\\
  %\affaddr{Research India}\\
 % \affaddr{New Delhi, India}\\
 % \email{author2@in.ibm.com}
}

%\date{25 March 2013}

\maketitle
\begin{abstract}
A news browser opening a newspaper or loading a news website jumps
into a story somewhere in the middle and is faced with the complex
task of figuring out the story's history and context(s). This task is
extremely difficult with current keyword search interfaces which
simply provide a list of articles. The complexity of the task is
compounded by the fact that different users are interest in different
contexts of the story, and it is impossible, {\em a priori} to guess
what a particular users interest may be. Our aim in this paper is to
present a news-browsing tools that allows for the complex task of
context creation, we call it {\em personalized flexible context
  extraction}, by preprocessing and storing articles in a structures
way that makes it easy for the user to explore different
contexts. Building on the work of Choudhary et. al. (ECIR, 2008) we
model the news corpus as a graph of interacting actors and topics,
each node being a news story. This graph is used as the backend to our
system, called ESTHETE.  Our approach involves spending computational
resources on preprocessing rather than processing. The advantage of
this approach is that the incremental computational expense in
incorporating new articles as they are published in minimal. This
approach marks a significant departure from much of the research on
news browsing in the literature which usually treats the entire corpus
as a semi-structured input when presented with individual queries. We
present several examples where ESTHETE can be used to follow stories
spanning many days or weeks. We also report on a detailed user
evaluation which highlights the usefulness of our system.

\end{abstract}

%{\bf MR: Abstract can be made tighter}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}[performance measures]

\terms{News Corpus Visualization, Flexible Personalized Context-rich News graph, News Summarization, System for News browsing, Interface Design}

%\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\input{intro}
\input{relwork}
\input{newsgraph}
\input{system}
\input{expts}
%\input{ack}
\input{conclusion}

\bibliographystyle{abbrv}
\bibliography{news}  % news.bib is the name of the Bibliography in this case


\end{document}
